European or American? A re-examination of the transatlantic influence over the IMF

### 2025-09-01 manuscript/manuscript.qmd
2nd para rephrased

>>>>

The results in @tbl-results-fiscal indicate that our earlier finding, that closer relations with the US, rather than European powers, are associated with fewer IMF conditions, extends to the *fiscal* subset of conditions. This echoes @guimaraes2021, who also find that political alignment with the US reduces fiscal conditions, though they do not control for European influence. Importantly, fewer fiscal conditions should not be taken as evidence of less stringent conditionality: our results on the required fiscal adjustment (RFA) are inconclusive, consistent with @guimaraes2021. Finally, fiscal-conditions data are available only from 1999 onwards, leaving a very limited sample ($N \approx 30$), so these findings should be interpreted with caution.
